EpisoPass: Password Management based on Episodic Memories

### 2016-08-26 paper/Password2016/paper.tex
...

However,
password-based authentication is still the most
convenient and strong method\cite{Bonnearu:ReplacePasswords},
and it is not supposed to get extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

@@

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}.
%
Password managers remember users' passwords and help them enter
passwords on various services.
%
%{\PW}管理システムは
%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
%暗号化されたデータベースに{\PW}を格納するもの%
%
Most password managers can manage various passwords by
asking users to remember a single ``master password'' to access the database.
%
%が多いが、サービス名をもとにマスター{\PW}を変換することによって
%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
%両者ともにマスター{\PW}の記憶は必須であり、
%マスター{\PW}を盗まれたり忘れたりする危険がある。
%
Although password managers are useful,
users have to remember the master password
or use a special hardware device
for safely handle password managers, and
password managers usually run on limited devices.

@@

If we don't want to carry any special device for authentication,
all the information required for the authentication should be
kept in the brain.
%
However, the biggest problem of brain-based authentication is that
users cannot safely keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories which they can never forget.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We propose a password manager \textit{EpisoPass} that generates strong passwords
based only on the user's secret episodic memories that the user can never forget.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
Memories in human brain are not uniform.
Some memories are very short-lived, and others are unforgettable.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily lose it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.
%

@@

@@

\item EpisoPass shows the data to the user so that
the user can select the right answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates
random-looking password candidate strings.
After selecting all the right answers,
the user copies the calculated string
and register it as the password for the service.
\end{enumerate}

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a random-looking string
based on the selections.
When the user selects the right answers to all the questions,
the right password is calculated and shown at the top.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
\caption{Generating a Twitter password with EpisoPass.}
\label{web1}
\end{figure}

@@

The second question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the last question is related to a more recent event
which the author thinks he can never forget.
All the questions are related to the author's episodic memories
that he thinks he never forgets, and nobody else knows which one of the
candidate answers is the right one.

@@

>>>>

However,
password-based authentication is still the most
convenient and strong method\cite{Bonnearu:ReplacePasswords},
and it is not supposed to become extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

@@

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}.
%
Password managers remember users' passwords and help them enter
passwords on various services.
%
%{\PW}管理システムは
%ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
%暗号化されたデータベースに{\PW}を格納するもの%
%
Most password managers can manage various passwords by
asking users to remember a single ``master password'' to access the database.
%
%が多いが、サービス名をもとにマスター{\PW}を変換することによって
%複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
%両者ともにマスター{\PW}の記憶は必須であり、
%マスター{\PW}を盗まれたり忘れたりする危険がある。
%
Although password managers are useful,
users have to remember the master password
or use a special hardware device
for safely handling password managers, and
password managers usually run on limited devices.

@@

If we don't want to carry any special device for authentication,
all the information required for the authentication should be
kept in the brain.
%
However, the biggest problem of brain-based authentication is that
users cannot safely keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories that they can never forget.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We propose a password manager \textit{EpisoPass} that generates strong passwords
based only on the user's secret episodic memories that the user cannot forget.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
% Memories in human brain are not uniform.
We keep various memories in our brain, but different memories have different natures.
Some memories are very short-lived, and others are unforgettable.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a new formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily lose it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.

@@

The idea of using episodic memories for authentication is not new.

**** Cognitive Passwords *******

@@

\item EpisoPass shows the data to the user so that
the user can select the right answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates
strong password candidate strings.
After selecting all the right answers,
the user copies the calculated string
and register it as the password for the service.
\end{enumerate}

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections.
When the user selects the right answers to all the questions,
the right password is calculated and shown at the top.

@@

\begin{figure}[H]
\centering
% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
\caption{Generating an Amazon password with EpisoPass.}
\label{web1}
\end{figure}

@@

The second question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the last question is related to a more recent event
which the author thinks he will never forget.
All the questions are related to the author's episodic memories
that he thinks he never forgets, and nobody else knows which one of the
candidate answers is the right one.

@@

\subsection{EpisoPass on browser extension}

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{figures/43272f2003ed8c78307110c621eb12e5}
\caption{Running EpisoPass on Browser Extension.}
\label{extension}
\end{figure}
